A unified model for parsing and sentence understanding

### 2016-03-14 writing/hard_stack_paper/paper.tex
Minor math improvements

\begin{gather}
\colvec{4}
    {\vec{i}}
    {\vec{f}_l}
    {\vec{f}_r}
    {\vec{o}}
= \sigma(
W_{\text{iffo}}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
)
\\
\vec{g}
= \tanh(
W_{g}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
)
\\
\vec{c} = \vec{f}_l * \vec{c}_s^{\,2} + \vec{f}_r * \vec{c}_s^{\,1} + \vec{i} * \vec{g}  
\\
\vec{h} = \vec{o} * \vec{c}
\end{gather}

The results of this function are the pair $(\vec{h}, \vec{c})$, which are placed back on the stack. The two input tree nodes popped off the stack are represented as the pairs $(\vec{h}^1_s, \vec{c}^{\,1}_s)$ and $(\vec{h}^2_s, \vec{c}^{\,2}_s)$. In addition, $\vec{e}$ is an optional input argument which is either the empty vector $[]$ or a vector from an external source like the tracking LSTM (see below). $*$ denotes the elementwise product. Each vector-valued variable listed here is of dimension $D$, except $\vec{e}$, which is of dimensions $D_t$, which can be chosen independently.

@@

\begin{equation}
\vec{x}_{classifier} = 
\colvec{4}
    {\vec{h}_{\text{premise}}}
    {\vec{h}_{\text{hypothesis}}}
    {\vec{h}_{\text{premise}} - \vec{h}_{\text{hypothesis}}}
    {\vec{h}_{\text{premise}} * \vec{h}_{\text{hypothesis}}}
\end{equation}

@@

\paragraph{Tracking left context for interpretation} Lexical ambiguity is omnipresent in natural language. Most words have multiple senses or meanings, and it is generally necessary to use the context in which a word occurs to determine which of its senses or meanings is meant in a given sentence. Simpler sequence-based sentence encoding models like the standard LSTM RNN have an advantage here: when a sequence-based model first processes a word (first incorporates it into a partial sentence representation), the model has access to a state vector that summarizes all of the words to the left of the current word, and that state vector can serve as a crude but effective form of context to help with disambiguation. In contrast, when standard tree-structured models first process a word, they only have access to the constituent that the word is merging with, which is strictly less than the sequence model has access to, and is often just a single additional word. Feeding a context representation from the tracking LSTM into the composition function is a simple and efficient way to mitigate this disadvantage of tree-structured models.

>>>>

\begin{gather}
\colvec{4}
    {\vec{i}}
    {\vec{f}_l}
    {\vec{f}_r}
    {\vec{o}}
= \sigma\left(
W_{\text{iffo}}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
\right)
\\
\vec{g}
= \tanh\left(
W_{g}
\colvec{3}
    {\vec{h}_s^1}
    {\vec{h}_s^2}
    {\vec{e}}
\right)
\\
\vec{c} = \vec{f}_l \odot \vec{c}_s^{\,2} + \vec{f}_r \odot \vec{c}_s^{\,1} + \vec{i} \odot \vec{g}  
\\
\vec{h} = \vec{o} \odot \vec{c}
\end{gather}

The results of this function are the pair $\langle\vec{h}, \vec{c}\rangle$, which are placed back on the stack. The two input tree nodes popped off the stack are represented as the pairs $\langle\vec{h}^1_s, \vec{c}^{\,1}_s\rangle$ and $\langle\vec{h}^2_s, \vec{c}^{\,2}_s\rangle$. In addition, $\vec{e}$ is an optional input argument which is either the empty vector $[]$ or a vector from an external source like the tracking LSTM (see below). $\odot$ denotes the elementwise product. Each vector-valued variable listed here is of dimension $D$, except $\vec{e}$, which is of dimensions $D_t$, which can be chosen independently.

@@

\begin{equation}
\vec{x}_{classifier} = 
\colvec{4}
    {\vec{h}_{\text{premise}}}
    {\vec{h}_{\text{hypothesis}}}
    {\vec{h}_{\text{premise}} - \vec{h}_{\text{hypothesis}}}
    {\vec{h}_{\text{premise}} \odot \vec{h}_{\text{hypothesis}}}
\end{equation}

@@

\paragraph{Tracking left context for interpretation} Lexical ambiguity is omnipresent in natural language. Most words have multiple senses or meanings, and it is generally necessary to use the context in which a word occurs to determine which of its senses or meanings is meant in a given sentence. Simpler sequence-based sentence encoding models like the standard LSTM RNN have an advantage here: when a sequence-based model first processes a word (first incorporates it into a partial sentence representation), the model has access to a state vector that summarizes all of the words to the left of the current word, and that state vector can serve as a crude but effective form of context to help with disambiguation. In contrast, when standard tree-structured models first process a word, they only have access to the constituent that the word is merging with, which is strictly less than the sequence model has access to, and is often just a single additional word. Feeding a context representation from the tracking LSTM into the composition function is a simple and efficient way to mitigate this disadvantage of tree-structured models.
\todo{Include figure of post-order traversal sequence made by the tracking LSTM?}
